---
title: 'Blog Post 4: Machine Learning'
author: "Jovanni Catalan Hurtado"
date: '2022-07-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r eval=FALSE}
## Render Code

rmarkdown::render("./_Rmd/2022-07-20-machine-learning-blog4.Rmd", 
                  output_format = "github_document",
                  output_dir = "./_posts",
                  output_options = list(
                    html_preview= FALSE
                    )
)  
```

## What method did you find most interesting?

I thought the Tree based methods were pretty interesting since the fits for these are a bit different. They split up the predictor space into regions and predict the most prevalent class for that region. I think that it would be pretty cool to see this in action in some sort of cool app or to see how it is applied in a field or profession and be able to test how well it  
performs there!




## Below is an example of a Classification Tree Fit
```{r}
library(tree)
library(dplyr)
set.seed(3)

train <- sample(1:nrow(iris), size = nrow(iris)*.80)

irisTrain <- iris[train, ]
irisTest <- iris[-train, ]

treeFit <- tree(Species ~ ., data = irisTrain)
treePred <- predict(treeFit, select(irisTest, -Species), type = "class")
treeRMSE <- table(data.frame(treePred, iris$Species))
treeRMSE

```
